---
title: "Homework 1"
author: Diana Sanchez
output: github_document
---

This is my solution to HW1.

``` {r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df =
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical, but not character or factor variables

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert logical and factor variables to numeric variables, but I can't do this for a character variable.

```{r eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

I can convert a logical variable to a numerical and then multiply it by the random sample, but I can't multiply factor variables by the random sample. However, I can convert the logical variable to a factor variable and then to numeric and then multiply by the random sample. However, this gives me a different result compared to converting the logical variable directly to a numeric variable.

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")

names(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm=TRUE)
summary(penguins)

```

The penguins dataset includes the 8 variables: "species", "island", "bill_length_mm", "bill_depth_mm", "flipper_length_mm", "body_mass_g", "sex", and "year". It includes 344 observations (rows), and, again 8 variables (columns). The mean flipper length, once the missing values were removed, is 200.9152 mm. Values for "species" in this data set include "Adelie", "Chinstrap", and "Gentoo". Also, values for "island" include "Biscoe", "Dream", and "Torgersen". 


```{r}
penguins %>%
    ggplot (aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point(alpha = .5) +
  geom_smooth(se = FALSE) +
  theme(legend.position = "bottom")
ggsave("penguins_scatter_plot.pdf", height = 4, width = 6)
```








